Block bootstrap consistency\\under weak assumptions

### 2015-12-31 Paper.tex
[#17] Fix small errors in proof of Lemma 5

\begin{proof}[Proof of~(\ref{eq:27})]
  We can express this summation as
  \begin{multline}\label{eq:29}
    \tfrac{1}{n} \sum_{\tau=0}^{n-1}  \sum_{j=1}^{J_n}
    \big\{Z_n'(\tau, M_{nj})^2 - \Em Z_n'(\tau, M_{nj})^2 \big\}
    \\ =
    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
    \sum_{i=0}^{L_{nj}-1}\big\{\big[ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n) + Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)\big]^2 \\
    - \Em\big[ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n) + Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)\big]^2 \big\} \\
    + \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau= M_{nj}L_{nj}}^{n-1}
    \big\{Z_{n}'(\tau, M_{nj})^2 - \Em Z_n'(\tau, M_{nj})^2 \big\}
  \end{multline}
  almost surely.
  By Lemma~\ref{dejong-restatement-lemma} (Equation~\ref{eq:32}), for
  any $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
  \begin{align*}
    \Big\lVert\tfrac{1}{n} \sum_{j=1}^{J_n} & \sum_{\tau=0}^{M_{nj}-1}
    \sum_{i=0}^{L_{nj}-1} \big\{ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2 -
    \Em \big(Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2\big) \big\}\Big\rVert_1 \\
    &\leq \E \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
    \Em \Big| \sum_{i=0}^{L_{nj}-1} \big\{ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2 -
    \Em \big(Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2\big) \big\} \Big|\\
    &\leq \E \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} 
    \big(2 \delta + C \, \tfrac{M_{nj}}{n^{1/2} \ell^{1/2+\epsilon}}\big)\Big)
  \end{align*}
  for large enough $n$, which converges to $2 \delta$ by
  Lemma~\ref{block-length-convergence-lemma}. Also,
  Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there
  exists a value $C$ (possibly different from the value above) such
  that
  \begin{equation*}
    \E\Big(\tfrac{1}{n}  \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} \sum_{i=0}^{L_{nj}-1}
    Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)^2 \Big)
    \leq C \E \Big(\sum_{j=1}^{J_n} L_{nj} \ell_n M_{nj} / n^2\Big)
  \end{equation*}
  and
  \begin{equation*}
    \E \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau= M_{nj}L_{nj}}^{n-1} Z_{n}'(\tau, M_{nj})^2\Big)
    \leq
    C \E \Big(\sum_{j=1}^{J_n} M_{nj}^2 / n^2 \Big)
  \end{equation*}
  for large enough $n$, both of which converge to zero in $L_1$ as $n
  \to \infty$ by Lemma~\ref{block-length-convergence-lemma}.  These
  three convergence results imply that the \textsc{rhs} of
  (\ref{eq:29}) converges to zero, completing the proof.
\end{proof}

\begin{proof}[Proof of~(\ref{eq:28})]
  After using similar arguments to in the previous part of the proof,
  the conclusion holds if
  \begin{equation*}
    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} \sum_{i=0}^{L_{nj} - 1}
    \Em Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2 \to^p \sigma^2,
  \end{equation*}
  which is a direct implication of Lemma~\ref{dejong-restatement-lemma}.
\end{proof}

\begin{lem}\label{bootstrapped-zsq-uniform-integrability-lemma}
  Under the conditions of Theorem~\ref{main-bootstrap-clt},
  \begin{multline}\label{eq:35}
    \lim_{C \to 0} \limsup_{n \to \infty} \sup_{m' = 1,\dots,n}
    \E\Big(\Big(\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'\Big) \\
    \times\ind\Big\{\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' > C\Big\}\Big) = 0.
  \end{multline}
  and
  \begin{multline}\label{eq:30}
    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
    \E\Big(\max_{m = 1,\dots,m'} (n \, Z^*_n(\tau, m)^2 / m') \\
    \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
    = 0,
  \end{multline}
  making the families of random variables $\{\max_{m=1,\dots,m'}
  Z_n(\tau, m)^2 n / m'\}$ and $\{\max_{m=1,\dots,m'}
  Z^{*}_n(\tau, m)^2 n / m'\}$ uniformly integrable.
\end{lem}

\begin{proof}
  For \eqref{eq:35}, take $\epsilon > 0$. The sum
  \[
  \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'
  \]
  is uniformly integrable if and only if it is uniformly $L_1$-bounded
  and there exists an $\epsilon'$ such that
  \[
  \sup_{n, m} \E\Big( \ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' \Big)
  < \epsilon
  \]
  for every event $A$ satisfying $\pr(A) < \epsilon'$.
  (\citealp{Dav:94}, 12.9.)
  Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there is an
  $\epsilon'$ such that
  \begin{equation*}
    \sup_{n, m', \tau} \E\big( \ind(A) \max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n / m' \big) \leq \epsilon / 9
  \end{equation*}
  for all $A$ with $\pr(A) \leq \epsilon'$. Then, writing
  \begin{align*}
    Z_n(\tau, m) &= Z_n'(\tau, m)
    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)}
    \big((\mu_{nt} - \bar \mu_n) + (\bar \mu_n - \bar X_n)\big) \\
    &= Z_n'(\tau, m)
    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n)
    - m Z'_n(0, n) \\
  \end{align*}
  gives the relationship
  \begin{align*}
    \E\Big(\ind(A) \sum_{\tau=0}^{n-1} & \max_{m=1,\dots,m'} Z_n(\tau, m)^2/m'\Big) \\
    &\leq 3 \sum_{\tau=0}^{n-1} \E\big( \ind(A)  \max_{m=1,\dots,m'} Z'_n(\tau, m)^2/m'\big) \\
    &\quad+(3/n m') \E\Big(\ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'}
    \Big(\sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n) \Big)^2\Big) \\
    &\quad+ (3/m') \sum_{\tau=0}^{n-1}
    \E (\ind(A) \max_{m=1,\dots,m'} m Z'_n(0, n)^2) \\
    &\leq (2 \epsilon/3) + \pr(A) (3/n)\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
  \end{align*}
  where the last inequality holds as a consequence of $A$'s
  construction. Since $(1/n)\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 \to
  0$, choose $n$ large enough that this average is less than
  $\epsilon/9$. The proof that that the first moment is bounded is
  similar, which completes the proof of~(\ref{eq:35})

  For~(\ref{eq:30}), we will first show that, for every $\epsilon > 0$,
  there exists an $\epsilon' > 0$ with the property that
  \begin{equation}\label{eq:31}
    \Em \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
  \end{equation}
  for any event $A \in \Gs \equiv \sigma(X_{11},\dots,X_{nn};\
  M_{n1},\dots,M_{n,J_n};\ J_n)$ with $\pr(A) \leq \epsilon'$. Then we
  will show that this property implies uniform integrability.%
\footnote{The difference between this proof and the proof
  of~\eqref{eq:35} is the measurability requirement. Here we need to
  finesse measurability of the sets $A$.} %

  Take an arbitrary $\epsilon > 0$ and a value of $\epsilon' > 0$
  so that
  \begin{equation*}
    \Em \Big(\ind(A) \sum_{\tau = 0}^{n-1} \tfrac{1}{m'} \max_{m = 1,\dots,m'}
    Z_n(\tau, m)^2\Big) < \epsilon / 4
  \end{equation*}
  for any $A \in \Gs$ with $\pr(A) \leq \epsilon'$, which is shown to
  exist in the first part of this Lemma. Then define $J(x)$ to be the
  block index such that $K_{n,J(x) - 1} < x \leq K_{n,J(x)}$. We have
  the relationships
  \begin{align*}
    \Em \Em^* \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big) \\
    &= \Em \ind(A) \Em^* \Big[ \tfrac{n}{m'}\max_{m = 1,\dots, m'}
    \Big(\sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*
    + Z_n^*(\tau, K_{n,J(\tau)} - \tau) \\
    &\quad+ Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}) \Big)^2\Big] \\
    &\leq 4 \Em \ind(A) \tfrac{1}{m'} \sum_{u = 0}^{n-1} \Big( \sum_{j=J(\tau)+1}^{J(\tau + m')-1}
    Z_n(u, M_{nj})^2 + Z_n(u, K_{n,J(\tau)} - \tau)^2 \\
    &\quad + Z_n(u, m' - K_{n,J(\tau+m')-1})^2\Big) \\
    &= (4/m') \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em\Big[ \ind(A) \sum_{u = 0}^{n-1} Z_n(u, M_{nj})^2\Big] \\
    &\quad + (4/m') \Em\Big[\ind(A) \sum_{u = 0}^{n-1} Z_n(\tau_{J(\tau)}, M_{n,J(\tau)})^2\Big] \\
    &\quad + (4/m') \Em\Big[ \ind(A)  \sum_{u = 0}^{n-1} Z_n(u, m' - K_{n,J(\tau+m')})^2\Big] \\
    &\leq \epsilon.
  \end{align*}
  The first inequality is a consequence of Doob's maximal inequality
  for martingales \citep[see][Theorem 15.15, for example]{Dav:94},
  since $Z_{nj}^*$ is a martingale difference array, and the second
  equality and last inequality follow by construction of $A$. A
  similar argument also implies that $n Z_n^*(\tau, m)^2 / m'$ has
  finite first moment.

  Now, for uniform integrability, take $\epsilon > 0$, choose
  $\epsilon'$ so that~\eqref{eq:31} holds for all $A \in \Gs$
  s.t. $\pr(A) \leq \epsilon'$, and choose $C_0$ large enough that
  \begin{equation*}
    \Pm\Big[ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C_0 \Big] \leq \epsilon'.
  \end{equation*}
  Markov's inequality guarantees the existence of this $C_0$. Then
  \begin{equation*}
    \Em \Big(\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'
    \times \ind\Big\{ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C \Big\}\Big) \leq \epsilon
  \end{equation*}
  for all $C > C_0$. Since $\epsilon$ is arbitrary, this completes the proof.
\end{proof}

>>>>

\begin{proof}[Proof of~(\ref{eq:27})]
  We can express this summation as
  \begin{multline}\label{eq:29}
    \tfrac{1}{n} \sum_{\tau=0}^{n-1}  \sum_{j=1}^{J_n}
    \big\{Z_n'(\tau, M_{nj})^2 - \Em Z_n'(\tau, M_{nj})^2 \big\}
    \\ =
    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
    \sum_{i=0}^{L_{nj}-1}\big\{\big[ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n) + Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)\big]^2 \\
    - \Em\big[ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n) + Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)\big]^2 \big\} \\
    + \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau= M_{nj}L_{nj}}^{n-1}
    \big\{Z_{n}'(\tau, M_{nj})^2 - \Em Z_n'(\tau, M_{nj})^2 \big\}
  \end{multline}
  almost surely.
  By Lemma~\ref{dejong-restatement-lemma} (Equation~\ref{eq:32}), for
  any $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
  \begin{align*}
    \Big\lVert\tfrac{1}{n} \sum_{j=1}^{J_n} & \sum_{\tau=0}^{M_{nj}-1}
    \sum_{i=0}^{L_{nj}-1} \big\{ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2 -
    \Em \big(Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2\big) \big\}\Big\rVert_1 \\
    &\leq \E \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
    \Em \Big| \sum_{i=0}^{L_{nj}-1} \big\{ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2 -
    \Em \big(Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2\big) \big\} \Big|\\
    &\leq \E \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
    \big(2 \delta + C \, \tfrac{M_{nj}}{n^{1/2} \ell^{1/2+\epsilon}}\big)\Big)
  \end{align*}
  for large enough $n$, which converges to $2 \delta$ by
  Lemma~\ref{block-length-convergence-lemma}.
  Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there
  exists a value $C$ (possibly different from the value above) such
  that
  \begin{align*}
    \E\Big(\tfrac{1}{n}  \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} \sum_{i=0}^{L_{nj}-1}
    & Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)^2 \Big) \\
    &= \E \Em \Big(\tfrac{1}{n}  \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} \sum_{i=0}^{L_{nj}-1}
    Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)^2 \Big) \\
    &\leq C \E \Big(\sum_{j=1}^{J_n} L_{nj} \ell_n M_{nj} / n^2\Big)
  \end{align*}
  and
  \begin{equation*}
    \E \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau= M_{nj}L_{nj}}^{n-1} Z_{n}'(\tau, M_{nj})^2\Big)
    \leq
    C \E \Big(\sum_{j=1}^{J_n} M_{nj}^2 / n^2 \Big)
  \end{equation*}
  for large enough $n$,%
\footnote{Lemma~\ref{dejong-restatement-lemma}
  and~\ref{zsq-uniform-integrability-lemma} are stated for the
  unconditional expectation, which may cause some confusion here. Note
  that $M_{nj}$ is measurable with respect to $\mathcal{M}_n$ and
  is treated the same as the constant $m$ in the statement of
  these Lemmas.  The other random variables in
  these expressions are independent of $\mathcal{M}_n$. So the only
  effect of conditioning on $\mathcal{M}_n$ is to prevent integration
  over the distributions of the $M_{nj}$ and the expectation otherwise
  behaves exactly like the unconditional expectation.\label{f:1}} %
  both of which converge to zero in $L_1$ as $n \to \infty$ by
  Lemma~\ref{block-length-convergence-lemma}.  These three convergence
  results imply that the \allcaps{rhs} of (\ref{eq:29}) converges to
  zero in probability, completing the proof.
\end{proof}

\begin{proof}[Proof of~(\ref{eq:28})]
  After using similar arguments to the previous part of the proof,
  the conclusion holds if
  \begin{equation*}
    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} \sum_{i=0}^{L_{nj} - 1}
    \Em Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2 \to^p \sigma^2,
  \end{equation*}
  which is a direct implication of
  Lemma~\ref{dejong-restatement-lemma}.%
  \footnote{The discussion in Footnote~\ref{f:1} applies here as well.}
\end{proof}

\begin{lem}\label{bootstrapped-zsq-uniform-integrability-lemma}
  Under the conditions of Theorem~\ref{main-bootstrap-clt},
  \begin{multline}\label{eq:35}
    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{m' = 1,\dots,n}
    \E\Big(\Big(\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'\Big) \\
    \times\ind\Big\{\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' > C\Big\}\Big) = 0.
  \end{multline}
  and
  \begin{multline}\label{eq:30}
    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
    \E\Big(\max_{m = 1,\dots,m'} (n \, Z^*_n(\tau, m)^2 / m') \\
    \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
    = 0,
  \end{multline}
  making the family of random variables $\{\max_{m=1,\dots,m'}
  Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ uniformly integrable.
\end{lem}

\begin{proof}
  For \eqref{eq:35}, take $\epsilon > 0$. The sum
  \[
  \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'
  \]
  is uniformly integrable if and only if it is uniformly $L_1$-bounded
  and there exists an $\epsilon'$ such that
  \[
  \sup_{n, m'} \E\Big( \ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' \Big)
  < \epsilon
  \]
  for every event $A \in \Omega_n$ satisfying $\pr(A) < \epsilon'$.
  (\citealp{Dav:94}, 12.9.)
  Lemma~\ref{zsq-uniform-integrability-lemma} ensures uniform integrability of
  $\max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n/m'$, so there exists an
  $\epsilon'$ such that
  \begin{equation*}
    \sup_{n, m', \tau} \E\big( \ind(A) \max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n / m' \big) \leq \epsilon / 9
  \end{equation*}
  for all $A \in \Omega_n$ with $\pr(A) \leq \epsilon'$. Then, writing
  \begin{align*}
    Z_n(\tau, m) &= Z_n'(\tau, m)
    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)}
    \big((\mu_{nt} - \bar \mu_n) + (\bar \mu_n - \bar X_n)\big) \\
    &= Z_n'(\tau, m)
    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n)
    - (m/n) Z'_n(0, n)
  \end{align*}
  gives the relationship
  \begin{align*}
    \E\Big(\ind(A) \sum_{\tau=0}^{n-1} & \max_{m=1,\dots,m'} Z_n(\tau, m)^2/m'\Big) \\
    &\leq 3 \sum_{\tau=0}^{n-1} \E\big( \ind(A)  \max_{m=1,\dots,m'} Z'_n(\tau, m)^2/m'\big) \\
    &\quad+(3/n m') \E\Big(\ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'}
    \Big(\sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n) \Big)^2\Big) \\
    &\quad+ (3 m' / n) \E (\ind(A) Z'_n(0, n)^2) \\
    &\leq (2 \epsilon/3) + (3 \epsilon' m' / n)\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
  \end{align*}
  where the last inequality holds as a consequence of $A$'s
  construction. Since $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 \to
  0$, choose $n$ large enough that this sum is less than
  $\epsilon/9\epsilon'$. The proof that that the first moment is bounded is
  similar, which completes the proof of~(\ref{eq:35}).

  For~(\ref{eq:30}), we will first show that, for every $\epsilon > 0$,
  there exists an $\epsilon' > 0$ with the property that
  \begin{equation}\label{eq:31}
    \Em \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
  \end{equation}
  for any event $A \in \Fs_n \equiv \sigma(X_{n1},\dots,X_{nn};\,
  M_{n1},\dots,M_{n,J_n};\, J_n)$ with $\pr(A) \leq
  \epsilon'$. Then we will show that this property implies uniform
  integrability.%
\footnote{The novelty in this part of the proof is the measurability
  requirement. The sigma-field $\Fs_n$ intentionally exlcudes the
  block start periods $u_{n1},\dots,u_{n,J_n}$, so
  $Z_n^{*}(\tau, m)^2$ is not $\Fs_n$-measureable. If we instead
  proved~\eqref{eq:31} for all $A \in \Omega_n$, as we did for the
  first part of the proof, then uniform integrebality would be an
  immediate consequence and would not need to be shown separately. See
  \citet[Theorem 12.9]{Dav:94}.} %

  Take an arbitrary $\epsilon > 0$ and a value of $\epsilon' > 0$
  so that
  \begin{equation*}
    \sup_{m'=1,\dots,n} \Em \Big(\ind(A) \sum_{\tau = 0}^{n-1} \tfrac{1}{m'} \max_{m = 1,\dots,m'}
    Z_n(\tau, m)^2\Big) < \epsilon / 6
  \end{equation*}
  for any $A \in \Fs_n$ with $\pr(A) \leq \epsilon'$, which is
  shown to exist in the first part of this Lemma. Then, for any $x$,
  define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
  \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$ as
  \begin{equation*}
  Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
  \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}),
  \end{equation*}
  giving
  \begin{align}
  \Em \Em^* \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big)
  \notag \\
  &\leq 3 \Em \Em^* \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big]
  \notag \\
  &\quad + 3 \Em \Em^* \big[\ind(A) \tfrac{n}{m'}
  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big]\label{eq:6}
  \end{align}
  almost surely.

  Since $Z_{nj}^*$ is a martingale difference array, Doob's maximal
  inequality for martingales \citep[see][Theorem 15.15, for
  example]{Dav:94} along with the construction of $Z_{nj}^{*}$ gives
  a bound for the first term on the \allcaps{RHS} of~\eqref{eq:6},
  \begin{multline*}
  \Em \Em^* \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big] \\
  \leq \tfrac{1}{m'} \sum_{u = 0}^{n-1} \Big\{\Em\big[\ind(A) Z_n(u, K_{n,J(\tau)} - \tau)^2\big] +
  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2]\Big\}
  \end{multline*}
  and this term is less than $\epsilon/6$ by construction of $A$.
  For the second term on the \allcaps{RHS}~\eqref{eq:6}, use the sequence of inequalities
  \begin{align*}
  \Em \Em^* \big[\ind(A) &\tfrac{n}{m'}
  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big] \\
  &\leq \sum_{j=J(\tau) + 1}^{J(\tau+m')-1} \tfrac{n}{m'} \Em \Em^* \big[\ind(A)
  \max_{m=1,\dots, \min(M_{nj}, m' - K_{n,j-1})} Z_n^*(K_{n,j}, m)^2 \big] \\
  &\leq \sum_{j=J(\tau) + 1}^{J(\tau+m')} \tfrac{M_{nj}}{m'} \sum_{u=0}^{n-1} \Em \big[\ind(A)
  \max_{m=1,\dots,\min(M_{nj}, m' - K_{n,j-1})} Z_n(u, m)^2 / M_{nj} \big] \\
  &\leq \sum_{j=J(\tau) + 1}^{J(\tau+m')} \epsilon \cdot \min(M_{nj}, m' - K_{n,j-1}) / 6 m' \\
  &\leq \epsilon/6.
  \end{align*}
  Together, these bounds imply~(\ref{eq:31}). A
  similar argument also implies that $n Z_n^*(\tau, m)^2 / m'$ has
  finite first moment.

  Now, for uniform integrability, take $\epsilon > 0$, choose
  $\epsilon'$ so that~\eqref{eq:31} holds for all $A \in \Fs_n$
  s.t. $\pr(A) \leq \epsilon'$, and choose $C_0$ large enough that
  \begin{equation*}
    \Pm\Big[ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C_0 \Big] \leq \epsilon'.
  \end{equation*}
  Markov's inequality guarantees the existence of this $C_0$. Then
  \begin{equation*}
    \Em \Big(\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'
    \times \ind\Big\{ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C \Big\}\Big) \leq \epsilon
  \end{equation*}
  for all $C > C_0$. Since $\epsilon$ is arbitrary, this completes the proof.
\end{proof}
